Will it blend: Is the Milky Way bar causing chaotic fanning of the Ophiuchus stream?

### 2015-09-05 ms.tex
refs

In both models, we use a spherical Navarro-Frenk-White potential to represent the dark matter \citep{nfw96}, a Miyamoto-Nagai potential for the disk \citep{miyamoto75}, and a Hernquist spheroid for the central spherical component of the bulge \citep{hernquist90}. Model A consists of just these three components and the total potential is therefore static and axisymmetric. Model B includes a component to represent the Galactic bar. For the bar component, we use a basis function expansion (BFE) of the potential and density of the bar with expansion coefficients derived for a triaxial, exponential bar density \citep[][hereafter W12]{wang12}. We use the pre-computed expansion coefficients used in W12, which were computed from a low-order expansion of the triaxial bar density used in \citet{dwek95}.\footnote{The coefficients presented in W12 are for just the cosine terms (the $A_{lm}$ in \citet{hernquist92} or the $S_{nlm}$ in \citet{lowing11}) because all sine terms have zero coefficients for a triaxial density function.} We have implemented the BFE computation of the potential, density, and gradient of the potential in C and Python and the code is publicly available on \project{GitHub}.\footnote{\url{https://github.com/adrn/biff}}

>>>>

In both models, we use a spherical Navarro-Frenk-White potential to represent the dark matter \citep{navarro96}, a Miyamoto-Nagai potential for the disk \citep{miyamoto75}, and a Hernquist spheroid for the central spherical component of the bulge \citep{hernquist90}. Model A consists of just these three components and the total potential is therefore static and axisymmetric. Model B includes a component to represent the Galactic bar. For the bar component, we use a basis function expansion (BFE) of the potential and density of the bar with expansion coefficients derived for a triaxial, exponential bar density \citep[][hereafter W12]{wang12}. We use the pre-computed expansion coefficients used in W12, which were computed from a low-order expansion of the triaxial bar density used in \citet{dwek95}.\footnote{The coefficients presented in W12 are for just the cosine terms (the $A_{lm}$ in \citet{hernquist92} or the $S_{nlm}$ in \citet{lowing11}) because all sine terms have zero coefficients for a triaxial density function.} We have implemented the BFE computation of the potential, density, and gradient of the potential in C and Python and the code is publicly available on \project{GitHub}.\footnote{\url{https://github.com/adrn/biff}}
